---
title: "Getting Started with oeis.tools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with oeis.tools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(oeis.tools)
```

## Introduction

`oeis.tools` is an R package designed to provide a seamless interface to the Online Encyclopedia of Integer Sequences (OEIS). It allows you to fetch sequence metadata, parse extensive b-files, and visualize sequences with ease.

## Fetching a Sequence

The core of the package is the `Sequence` class. You can fetch any sequence using its OEIS ID (e.g., A000045 for Fibonacci numbers).

```{r fetch-example, eval = FALSE}
# Fetch the Fibonacci sequence
fib <- Sequence("A000045")

# Access basic information
fib$id
fib$name
```

## Working with B-files

B-files provide a way to access thousands of terms of a sequence, which are often not fully available in the main OEIS entry.

```{r bfile-example, eval = FALSE}
# Get b-file data for Prime numbers
primes_bfile <- BFile("A000040")

# Access the data
data <- get_bfile_data(primes_bfile)
length(data)
```

## Visualization

The package integrates with `ggplot2` to provide instant visualizations.

```{r plot-example, eval = FALSE}
# Plot the first 100 terms of the Fibonacci sequence from its b-file
plot_data(primes_bfile, n = 100, color = "darkgreen")
```

## Extracting Cross-References

You can find related sequences using `get_xref_ids()`:

```{r xref-example, eval = FALSE}
# Get related sequences for Fibonacci
get_xref_ids(fib)
```

## Keyword Descriptions

OEIS uses various keyword tags. You can get a human-readable description for these:

```{r keyword-example}
oeis_keyword_description("core")
oeis_keyword_description("nice")
```
